`forestecology` package for modeling interspecies competition between trees

### 2021-01-15 README.Rmd
adjust output of predict method

```{r}
# Fit model
posterior_param_ex <- focal_vs_comp_ex %>%
  fit_bayesian_model(prior_param = NULL, run_shuffle = FALSE)

# Get predicted dbh values values
predictions <- focal_vs_comp_ex %>%
  predict_bayesian_model(posterior_param = posterior_param_ex) %>%
  right_join(ex_growth_df, by = c("focal_ID" = "ID"))

# Compute RMSE of true vs predicted dbh values
predictions %>%
  rmse(truth = growth, estimate = growth_hat) %>%
  pull(.estimate)

@@

# Compute RMSE of true vs predicted dbh values
ex_bw %>%
  rmse(truth = growth, estimate = growth_hat) %>%
  pull(.estimate)
```

>>>>

```{r}
# Fit model
posterior_param_ex <- focal_vs_comp_ex %>%
  fit(prior_param = NULL, run_shuffle = FALSE)

# Get predicted dbh values values
predictions <- focal_vs_comp_ex %>%
  predict(posterior_param = posterior_param_ex) %>%
  right_join(ex_growth_df, by = c("focal_ID" = "ID"))

# Compute RMSE of true vs predicted dbh values
predictions %>%
  rmse(truth = growth, estimate = .pred) %>%
  pull(.estimate)

@@

# Compute RMSE of true vs predicted dbh values
ex_bw %>%
  rmse(truth = growth, estimate = .pred) %>%
  pull(.estimate)
```

### 2021-01-15 etc/paper/forestecology.Rmd
fixed header error
adjust output of predict method

# Add foldID to each tree
```{r}
bw_growth_df <- bw_growth_df %>%
  mutate(foldID = bw_spatialBlock$foldID)
```

@@

# Remove empty folds

@@

```{r bw-model-rmse}
predictions %>%
  yardstick::rmse(truth = growth, estimate = growth_hat) %>%
  pull(.estimate)
```

@@

```{r bw-model-shuffle-rmse}
predictions_shuffle %>%
  rmse(truth = growth, estimate = growth_hat) %>%
  pull(.estimate)
```

@@

```{r scbi-model-rmse}
scbi_growth_df_noCV %>%
  rmse(truth = growth, estimate = growth_hat) %>%
  pull(.estimate)
```

@@

```{r scbi-model-residuals, out.width="100%", fig.cap="Predicted versus observed growth.", echo = FALSE}
ggplot(scbi_growth_df_noCV, aes(x = growth, y = growth_hat)) +
  geom_point(size = 0.5, color = rgb(0, 0, 0, 0.25)) +
  stat_smooth(method = "lm") +
  geom_abline(slope = 1, intercept = 0) +
  coord_fixed() +
  labs(
    x = "Observed growth in dbh", y = "Predicted growth in dbh",
    title = "Predicted vs Observed Growth"
  )
```

```{r scbi-model-residuals-2, out.width="80%", fig.cap="Spatial distribution of residuals for model applied to SCBI data.", echo = FALSE}
scbi_growth_df_noCV %>%
  st_as_sf() %>%
  # TODO: Need to investigate missingness
  filter(!is.na(growth_hat)) %>%
  mutate(
    error = growth - growth_hat,
    error_bin = cut_number(error, n = 5),
    error_compress = ifelse(error < -0.75, -0.75, ifelse(error > 0.75, 0.75, error))
  ) %>%
  ggplot() +
  geom_sf(aes(col = error_compress), size = 1) +
  theme_bw() +
  scale_color_gradient2(
    low = "#ef8a62", mid = "#f7f7f7", high = "#67a9cf",
    name = expression(paste("Residual (cm ", y^{-1}, ")")),
    breaks = seq(from = -0.75, to = 0.75, by = 0.25),
    labels = c("< -0.75", "-0.5", "0.25", "0", "0.25", "0.5", "> 0.75")
  ) +
  labs(x = "Meter", y = "Meter")
```

@@

cv_bw %>%
  rmse(truth = growth, estimate = growth_hat) %>%
  pull(.estimate)
```

@@

cv_scbi %>%
  rmse(truth = growth, estimate = growth_hat) %>%
  pull(.estimate)
```

>>>>

Then add foldID to each tree

```{r}
bw_growth_df <- bw_growth_df %>%
  mutate(foldID = bw_spatialBlock$foldID)
```

@@

Then remove empty folds

@@

```{r bw-model-rmse}
predictions %>%
  yardstick::rmse(truth = growth, estimate = .pred) %>%
  pull(.estimate)
```

@@

```{r bw-model-shuffle-rmse}
predictions_shuffle %>%
  rmse(truth = growth, estimate = .pred) %>%
  pull(.estimate)
```

@@

```{r scbi-model-rmse}
scbi_growth_df_noCV %>%
  rmse(truth = growth, estimate = .pred) %>%
  pull(.estimate)
```

@@

```{r scbi-model-residuals, out.width="100%", fig.cap="Predicted versus observed growth.", echo = FALSE}
ggplot(scbi_growth_df_noCV, aes(x = growth, y = .pred)) +
  geom_point(size = 0.5, color = rgb(0, 0, 0, 0.25)) +
  stat_smooth(method = "lm") +
  geom_abline(slope = 1, intercept = 0) +
  coord_fixed() +
  labs(
    x = "Observed growth in dbh", y = "Predicted growth in dbh",
    title = "Predicted vs Observed Growth"
  )
```

```{r scbi-model-residuals-2, out.width="80%", fig.cap="Spatial distribution of residuals for model applied to SCBI data.", echo = FALSE}
scbi_growth_df_noCV %>%
  st_as_sf() %>%
  # TODO: Need to investigate missingness
  filter(!is.na(.pred)) %>%
  mutate(
    error = growth - .pred,
    error_bin = cut_number(error, n = 5),
    error_compress = ifelse(error < -0.75, -0.75, ifelse(error > 0.75, 0.75, error))
  ) %>%
  ggplot() +
  geom_sf(aes(col = error_compress), size = 1) +
  theme_bw() +
  scale_color_gradient2(
    low = "#ef8a62", mid = "#f7f7f7", high = "#67a9cf",
    name = expression(paste("Residual (cm ", y^{-1}, ")")),
    breaks = seq(from = -0.75, to = 0.75, by = 0.25),
    labels = c("< -0.75", "-0.5", "0.25", "0", "0.25", "0.5", "> 0.75")
  ) +
  labs(x = "Meter", y = "Meter")
```

@@

cv_bw %>%
  rmse(truth = growth, estimate = .pred) %>%
  pull(.estimate)
```

@@

cv_scbi %>%
  rmse(truth = growth, estimate = .pred) %>%
  pull(.estimate)
```
